%!TEX TS-program = xelatex
\documentclass[]{friggeri-cv}
\addbibresource{bibliography.bib}

\begin{document}
\header{tim}{suchanek}
       {web developer}


% In the aside, each new line forces a line break
\begin{aside}
  \section{kontakt}
    Rankestrasse 2
    76137 Karlsruhe
    Germany
    ~
    \href{mailto:tim.suchanek@gmail.com}{tim.suchanek@gmail.com}
    \href{http://timsuchanek.de}{http://timsuchanek.de}
    \href{https://github.com/timsuchanek/}{github: timsuchanek}
    \href{https://twitter.com/timsuchanek}{twitter: @timsuchanek}
  \section{languages}
    german
    fluent english
    italian notions
  \section{programming}
    {\color{red} $\varheartsuit$} JavaScript
    (ES5/6/7, Node.js)
    Java, C, Ruby
    CSS3 \& HTML5
\end{aside}

\section{interests}

angular.js, mongodb, mongoose, express.js, redis, leveldb, asynchrone message queues, nosql/relational databases, es6 promises/generators, sharing economy, startups, ui algorithms, graphen algorithms

\section{education}

\begin{entrylist}
  \entry
    {2011 - expected 2015}
    {B.Sc. Computer Science}
    {Karlsruhe Institut für Technologie}
    {With focus on Cryptography, Cognitive Systems and Operations Research}
  \entry
    {07/2011}
    {Abitur}
    {Gesamtschule Eckenhagen}
    {1.6, valedictorian}
\end{entrylist}

\section{experience}

\begin{entrylist}
  \entry
    {08/2010 - 02/2012}
    {Flyingmedia Film Agency, Bergneustadt}
    {Internship.}
    {\emph{Creating IP-TV Platforms on PHP/SQL.}}
  \entry
    {02/2013 - 02/2014}
    {SAP, Walldorf}
    {Working Student.}
    {\emph{Developing an ORM and a student management app based on SAP HANA and XSScript}}
  \entry
    {02/2012 - 06/2012}
    {selfemployed}
    {Webdesign freelancer.}
    {\emph{Working for BRH, huge Drilling company from Germany}}
  \entry
    {07/2012 - 12/2012}
    {selfemployed}
    {Webdesign freelancer.}
    {\emph{Creating Immodraft, a real estate platform}}
  \entry
    {12/2012 - 06/2013}
    {selfemployed}
    {Webdesign freelancer.}
    {\emph{Creating an online shop for vinoko.de based on ShopWare}}
  \entry
    {12/2011 - 06/2012}
    {Spoonbrain}
    {founder.}
    {\emph{Working at spoonbrain, an online platform for video tutorials}}
  \entry
    {12/2013 - now}
    {crowddining}
    {founder.}
    {\emph{Creating the whole platform crowddining.de with full stack JavaScript}}
\end{entrylist}

\section{applications}

\begin{entrylist}
  \entry
    {2013}
    {StopIt}
    {\href{https://play.google.com/store/apps/details?id=de.timsuchanek.stopit&hl=en}{StopIt on Google Play}}
    {Productivity app for android, that captures your usage time of other apps.}
  \entry
    {2013}
    {KVV prototype}
    {\href{http://schickling.github.io/kvv}{schickling.github.io/kvv}}
    {A prototype for a live train map of the KVV from Karlsruhe.}
  \entry
    {2014}
    {Crowddining}
    {\href{http://crowddining.de}{crowddining.de}}
    {An online platform to cook meals for other people. Including a NP-hard algorithm for the event \emph{Run&Eat} where chefs are matched}
\end{entrylist}

\section{competitions}

\begin{entrylist}
  \entry
    {2010}
    {Halbmarathon Bonn Kottenforst}
    {Bonn Kottenforst}
    {Time: 1:40}
  \entry
    {04 2011}
    {Halbmarathon Bonn}
    {Bonn}
    {Time: 1:38}
  \entry
    {10 2011}
    {Halbmarathon Köln}
    {Köln}
    {Time: 1:38}
  \entry
    {11 2013}
    {Startup Live Karlsruhe}
    {Karlsruhe}
    {1. place with team meet&eat}
  \entry
    {01 2014}
    {Elevator Pitch Baden Württemberg}
    {Karlsruhe}
    {3. place with crowddining}
  \entry
    {02 2014}
    {PG Grow}
    {Karlsruhe}
    {2. place with crowddining}
\end{entrylist}

